Fixed-Shape Ellipse by Three Points

### 2019-11-04 ONPCE/slides.tex

	\begin{frame}[t,plain]
		\titlepage
	\end{frame}

@@

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol3}
		\caption{After scaling.}
		\label{fig:sol33}
	\end{figure}
\end{frame}

@@

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol4}
		\caption{One solution for this instance.}
		\label{fig:sol4}
	\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item It can be written as 
		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
		\item The roots of $\xi$ are solutions of our problem.	
\end{itemize}

>>>>

	\begin{frame}[t,plain]
		\titlepage

		\footnotesize This research has been funded by Cordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES). This is part of a Master's research project on the problem: \textit{Planar Maximal Covering by Ellipses with Rotation}.
	\end{frame}

@@

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol3}
		\caption{After scaling by $\frac{b}{a}$.}
		\label{fig:sol33}
	\end{figure}
\end{frame}

\begin{frame}{Transforming the problem}
	Then, we apply the inverse transformation.

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol31}
		\caption{After scaling by $\frac{a}{b}$.}

@@

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol4}
		\caption{A solution is obtained after scaling by $\frac{a}{b}$ and rotating by $-\theta$.}
		\label{fig:sol4}
	\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item It can be written as 
		$$\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
		\item The roots of $\xi$ are solutions of our problem.	
\end{itemize}
